\documentclass[12pt]{article}

\begin{document}

\pagestyle{empty} % Removes page numbering

%%
%% Cover Letter
%%

My name is Alan, and I have been fascinated with computers for most of my life.
I got my first laptop when I was 12, and broke it when I was 13 by setting and
then incorrectly removing a BIOS password, which cost me a trip to a computer
repair store - my first interaction with such a place. I was amazed at the idea
of people fixing or modifying computers, and the idea stuck. Since then I've
never been back, electing to fix the problem myself. Some time shortly after, I
figured out what exactly NOT to uninstall by removing my Atheros network
driver. I fixed it easily, because I knew about the Windows system restore
functionality (probably from previous mistakes in a similar vein). This victory
only planted further how much I wanted to keep trying and learning things. At
14 I got a laptop with a disc drive, and I started testing out Linux
distributions in my spare time. Back when it was common to burn them to discs,
I had a 10-cd case all loaded up with different distros. My parents and
grandparents started to notice my abilities with computers and would ask for
help, anything from printer connectivity to simply using a web browser. I
became intimately familiar with what the control panel had to offer - I was
absolutely obsessed with settings and configuration.

\medskip

Now that I'm older, I have had more opportunities for bigger things. I built my
first desktop computer in 2015 out of some friends' old parts, and once I saved
up a bit more I started replacing them with newer and more powerful components.
I collect and restore old Thinkpads by giving them SSD's and more ram,
sometimes also getting a new keyboard that hasn't worn down so much. On my
personal favorite laptop, an x200, I have flashed a custom BIOS onto the chip
with a raspberry pi to make it boot faster. Funny enough, before I did this I
had to remove the supervisor password locking the old BIOS so I could update
the embedded controller firmware. I did this by bridging two pins on the little
BIOS chip at a perfect timing - this is probably one of my favorite
accomplishments as it wraps full circle with my first major screw up. I have a
soldering iron and a decent tool kit which I have used for repairs, like when
my friend broke their power button and I replaced the power board.

\medskip

I would love to have the opportunity to use my experience working on computers
to assist you in your store. It would be my absolute pleasure to use that
experience to further my own abilities, and use them in a productive
environment. I hope you consider my application, and I appreciate your time in
reading this. Have a wonderful day, and I hope to hear back from you!

\end{document}
